Categorical and gradient aspects of wordlikeness\thanks{Thanks to Gene Buckley, Charles Yang, and audiences at NELS 43 for helpful comments.}

### 2012-11-11 abs.tex
Completed writing on 2-4!

This dissertation argues for that phonotactic knowledge is primarily derived not from static generalizations but rather from phonological alternations and prosodic parsing. Chapter \ref{intro} outlines the proposal, historical precursors, and predictions. 
%especially with regards to order of acquisition.

>>>>

This dissertation outlines a program for phonotactic theory---the theory of speakers' language-specific knowledge of possible and impossible (or likely and unlikely) words---minimizing undue \emph{duplication} (in the sense of \citeboth{KK77}:136f.) between phonotactics and phonology, and shows that the alternative view of phonotactics as stochastic, and of phonotactic learning as probabilistic inference, is incapable of accounting for the facts of this domain.
Chapter \ref{intro} outlines the proposal, historical precursors, and predictions. 
%especially with regards to order of acquisition.

### 2012-11-11 ms2.tex
Completed writing on 2-4!

\abstract{Gradient ratings are a property of ratings tasks, not of the grammatical system itself.}

\input{2}
\appendix
\renewcommand{\arraystretch}{0.25}

@@

For every entry in the CELEX database, there is a corresponding broad syllabified transcription of the word in a Received Pronunciation accent. This appendix describes an automated procedure used to process these transcripts and to separate medial clusters from their flanking nuclei, parsing the resulting sequences into coda and onset, and reversing allophonic processes targeting medial clusters.

While the segmental content of these transcriptions is precise, the CELEX syllabifications are unsystematic. Given the absence of contrastive syllabification in English (if not all languages: see \citealp[221]{Blevins1995}, \citealp{Elfner2006}), any sequence of a medial consonant cluster and its flanking nuclei should receive the same syllabification in all words in which it occurs. This is not always the case with the CELEX transcriptions, however. For instance, the sequence [ɪstɹɪ] receives a different parse in \emph{chemistry} [ˈkɛ.mɪ.stɹɪ] and \emph{ministry} [ˈmɪ.nɪs.tɹɪ].\footnote{Note that word-final \emph{y} is lax in Received Pronunciation \citep[][II.294]{AOE}.}

@@

In English, when a medial consonant cluster is preceded by a stressed lax vowel, as \emph{wh}[ɪs.p]\emph{er}, \emph{v}[ɛs.t]\emph{ige}, or \emph{m}[ʌs.k]\emph{et}, the first consonant of the cluster checks the lax vowel \citep[3]{Hammond1997}. As \citet[55]{Harris1994} notes, however, when the medial cluster is also a valid onset, as in \emph{whi}[s.p]\emph{er}, \emph{ve}[s.ti]\emph{ge}, and \emph{mu}[s.k]\emph{et}, onset maximization will incorrectly assign the entire cluster to the onset and leave the lax vowel unchecked. For this reason, onset maximization parses are modified to assign the first consonant of a complex medial consonant cluster to the coda before a stressed lax vowel \citep[48]{Pulgram1970}.

@@

The traditional analysis of affricates as single segments (e.g., \emph{SPE}:321f., \citealp[24]{Jakobson1961}) rather than stop-fricative sequences \citep[e.g.,][]{Hualde1988,Lombardi1990} is assumed here. In many languages, affricates pattern with simple onsets; for instance, Classical Nahua bans true onset clusters but permits the affricate series [ts, tʃ, tɬ] \citep[9]{Launey2011}. In English, however, affricates do not form complex onsets. Yet, the stop and release phase of affricates cannot be separated by a syllable boundary, as predicted from the assumption they are single phonological units.

>>>>

\abstract{
Gradient wordlikeness judgements do not necessarily imply that a gradient well-formedness system underlies them; gradient judgements may be an artifact of gradient rating tasks.
Dubious architectural assumptions are needed for speakers to report gradient well-formedness judgements.
Simple baselines better account for gradient well-formedness judgements than state-of-the-art computational models of gradient phonotactic knowledge.
}
\section{Introduction}
\input{2}
\appendix
\renewcommand{\arraystretch}{0.25}

@@

This appendix describes an automated procedure used to process the CMU pronunciation dictionary entries, separating medial clusters from their flanking nuclei, parsing the resulting sequences into coda and onset, and reversing allophonic processes targeting medial clusters.

@@

In English, when a medial consonant cluster is preceded by a stressed lax vowel, as \emph{wh}[ɪs.p]\emph{er}, \emph{v}[ɛs.t]\emph{ige}, or \emph{m}[ʌs.k]\emph{et}, the first consonant of the cluster checks the lax vowel (\citealp[3]{Hammond1997}, \citealp{Treiman1990}). As \citet[55]{Harris1994} notes, however, when the medial cluster is also a valid onset, as in \emph{whi}[s.p]\emph{er}, \emph{ve}[s.ti]\emph{ge}, and \emph{mu}[s.k]\emph{et}, onset maximization will incorrectly assign the entire cluster to the onset and leave the lax vowel unchecked. For this reason, onset maximization parses are modified to assign the first consonant of a complex medial consonant cluster to the coda before a stressed lax vowel \citep[48]{Pulgram1970}.

@@

The traditional analysis of affricates as single segments (e.g., \emph{SPE}:321f., \citealp[24]{Jakobson1961}) rather than stop-fricative sequences \citep[e.g.,][]{Hualde1988,Lombardi1990} is assumed here. In many languages, affricates pattern with simple onsets; for instance, Classical Nahua bans true onset clusters but permits the affricate series [ts, tʃ, tɬ] \citep[9]{Launey2011}. In English, however, affricates do not form complex onsets. Yet the stop and release phase of affricates cannot be separated by a syllable boundary, as predicted from the assumption they are single phonological units.
